---
title: "Dagda"
output: html_document
---

```{r}
# --- Wish list
# integrate font from https://www.gaelchlo.com/suitlinux.html
# Report card - you got x percent, you need to work on y
# Resource for fadas
# Events
# Grammar Terminology
# chat bot, tell me everything you know about x word
# pick your activities for the day - give vocab for those
# Living in Ireland / going around Ireland (irish signs and place names)
# irish genetics facts
# Information on the types of words (e.g. verbal noun) and their name in irish and english
# irish history facts
# resources
# phrases i've found/heard on social media / using your phone as gaeilge
# license and acknowledgments
# put in a feature where someone picks an area on the map and I extract the name of towns in the area - i look for all towns in that area and then I tell you what the irish says about the landscape
# #dbWriteTable(con, "words", combined) - for faster running make an SQL database
```

Let's import some data we've processed:

```{r}
library(here)
word_data <- list(
  terminology = readRDS(here('data', 'tearma.rda')),
  frequency = readRDS(here('data', 'corpus.rda')),
  anki = readRDS(here('data', 'anki.rda')),
  frequency.guide = readRDS(here('data', 'corpus.pos.rda')))
```

```{r}
library(reticulate)
# ---- Load data on similar words based on meaning and morphology 
source('/home/shane/Desktop/files/current-projects/dagda/R/load_vectors.R')
similar = load_vectors()
```

Let's start with the top 500 terms from Anki

```{r}
library(dplyr)
test_data <- head(word_data$anki, 100)
test_data = merge(test_data, word_data$frequency, by.x='ga', by.y='word_form')
```

Now we will explore how to clean this up

```{r}
test_data <- test_data[order(as.integer(test_data$rank)),
            c('ga','en', 'lemma', 'rank',
              'pos','part_of_speech', 'gender','genitiveVN')]
```

```{r}

```


## Cuardach Comhchoiteann

<p><strong>Word:</strong>
<input type="text" id="searchWordUnified" placeholder="Enter a word here"></p>

<p><strong>Select dictionary:</strong>
<select id="dictionaryChoice">
  <option value="teanglann-ga">Teanglann (Irish → English, 1977)</option>
  <option value="focloir-ei">Foclóir.ie (English → Irish, 2013)</option>
  <option value="teanglann-ei">Teanglann (English → Irish, 1959)</option>
</select></p>

<button onclick="searchUnified()">Search</button>

<script>
  function searchUnified() {
    var word = document.getElementById("searchWordUnified").value.trim();
    var dict = document.getElementById("dictionaryChoice").value;

    if (word === "") {
      alert("Please enter a word.");
      return;
    }

    let url;
    switch (dict) {
      case "teanglann-ga":
        url = "https://www.teanglann.ie/en/fgb/" + encodeURIComponent(word);
        break;
      case "focloir-ei":
        url = "https://www.focloir.ie/en/dictionary/ei/" + encodeURIComponent(word);
        break;
      case "teanglann-ei":
        url = "https://www.teanglann.ie/en/eid/" + encodeURIComponent(word);
        break;
      default:
        alert("Invalid dictionary selection.");
        return;
    }

    window.open(url, "_blank");
  }
</script>


<!-- Include jQuery and Teanglann's An Foclóirí plugin -->
<script src="https://code.jquery.com/jquery-3.6.0.min.js"></script>
<script src="https://www.teanglann.ie/cab/cab.js"></script>
<script>
  jQuery(document).ready(function(){
    cab.clickify(); // Apply to entire page
  });
</script>


